### 2017-04-12 paper/oopsla17-submission/learning.tex

A multi-layered perceptron can be represented as a directed acyclic graph whose nodes are arranged in layers that are fully connected by weighted edges. The first layer corresponds to the input features, and the final to the output. The output of a node $v$ in layer $l$ is given by:
\[ h_v = g(\sum_{j \in N(v)} W_{jv} h_j ) \]
where $N(v)$ is the set of nodes in the previous layer that are adjacent to $v$, $W_{jv}$ is the weight of the $(j, v)$ edge and $h_j$ is the output of node $j$ in the previous layer. Finally $g$ is a non-linear function, called the activation function, which in recent work is commonly chosen to be the \emph{rectified linear unit} (ReLU),
defined as $g(x) = \mathsf{max}(0,x)$ \citep{Nair2010-xg}. The number of layers, the number of neurons per layer, and the connections between layers constitute the \emph{architecture} of a neural network. In our work, we use relatively simple neural networks which have an input layer, a single hidden layer and an output layer.

HEREHERE
%
%Neural networks can be understood as a collection of linear models, just
%like the one used in logistic regression, arranged in a directed graph.
%
%Each node in the graph corresponds to a single linear model, called a
%\emph{neuron}, and the edges propagate signals from the input features,
%through the neurons, to the output labels.
%
%The linear model in each neuron is wrapped in an \emph{activation
%  function}, which controls whether (or how strongly) the signal will be
%propagated out.
%
%These activation functions are what allow neural networks to accurately
%model nonlinear functions.
%
%A common choice of activation function is the same sigmoid function used
%by logistic regression, alternatives include the hyperbolic $\tanh$
%function, and more recently the \emph{rectified linear unit} (ReLU),
%defined as $f(x) = \mathsf{max}(0,x)$ \citep{Nair2010-xg}.

@@

%Neural networks are popular for their ability to uncover ``hidden''
%features in the data.
%
Each neuron learns a different linear combination of the signals from
the previous layer; combined with the activation function this can be
thought of as the neuron learning to respond to a new, \emph{compound}
feature of its inputs.
%
This ability to discover interesting combinations of features makes
neural networks easier to use in some respect; they can reduce the
importance of manual \emph{feature engineering} (selecting interesting
features to provide as inputs).
%
However, the sheer size and complexity of neural networks makes the
model particularly difficult to interpret --- they are generally regarded
as ``black boxes.''
%
Neural networks are also very susceptible to overfitting, so
regularization methods like the $L_2$ norm used for logistic regression
are important.

\ES{should mention that logistic regression can be thought of as a degenerate MLP with 0 layers, and perhaps add a diagram?}

\ES{need to say something about neurons corresponding to ``hidden'' features, give intuition..}

>>>>

A multi-layered perceptron can be represented as a directed acyclic graph whose nodes are arranged in layers that are fully connected by weighted edges. The first layer corresponds to the input features, and the final to the output. The output of a node $v$ in an internal layer is given by:
\[ h_v = g(\sum_{j \in N(v)} W_{jv} h_j ) \]
where $N(v)$ is the set of nodes in the previous layer that are adjacent to $v$, $W_{jv}$ is the weight of the $(j, v)$ edge and $h_j$ is the output of node $j$ in the previous layer. Finally $g$ is a non-linear function, called the activation function, which in recent work is commonly chosen to be the \emph{rectified linear unit} (ReLU),
defined as $g(x) = \mathsf{max}(0,x)$ \citep{Nair2010-xg}. The number of layers, the number of neurons per layer, and the connections between layers constitute the \emph{architecture} of a neural network. In this work, we use relatively simple neural networks which have an input layer, a single hidden layer and an output layer.

A major advantage of neural networks is its ability to discover interesting combinations of features through non-linearity, which significantly reduces the need for manual feature engineering, and allows high expressivity. On the other hand, this makes the networks particularly difficult to interpret and also difficult to generalize under vast amounts of training data are available.

%HEREHERE
%
%Neural networks can be understood as a collection of linear models, just
%like the one used in logistic regression, arranged in a directed graph.
%
%Each node in the graph corresponds to a single linear model, called a
%\emph{neuron}, and the edges propagate signals from the input features,
%through the neurons, to the output labels.
%
%The linear model in each neuron is wrapped in an \emph{activation
%  function}, which controls whether (or how strongly) the signal will be
%propagated out.
%
%These activation functions are what allow neural networks to accurately
%model nonlinear functions.
%
%A common choice of activation function is the same sigmoid function used
%by logistic regression, alternatives include the hyperbolic $\tanh$
%function, and more recently the \emph{rectified linear unit} (ReLU),
%defined as $f(x) = \mathsf{max}(0,x)$ \citep{Nair2010-xg}.

@@

%Neural networks are popular for their ability to uncover ``hidden''
%features in the data.
%
%Each neuron learns a different linear combination of the signals from
%the previous layer; combined with the activation function this can be
%thought of as the neuron learning to respond to a new, \emph{compound}
%feature of its inputs.
%
%This ability to discover interesting combinations of features makes
%neural networks easier to use in some respect; they can reduce the
%importance of manual \emph{feature engineering} (selecting interesting
%features to provide as inputs).
%
%However, the sheer size and complexity of neural networks makes the
%model particularly difficult to interpret --- they are generally regarded
%as ``black boxes.''
%
%Neural networks are also very susceptible to overfitting, so
%regularization methods like the $L_2$ norm used for logistic regression
%are important.

%\ES{should mention that logistic regression can be thought of as a degenerate MLP with 0 layers, and perhaps add a diagram?}

%\ES{need to say something about neurons corresponding to ``hidden'' features, give intuition..}
